---
title: "Street Playing Card Simulation Problem"
author: "Michelle Alexander"
date: "30/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Problem

Over the past four years I have collected playing cards I found on the street. In this time I have collected 16 of unique suit and value, and 18 total cards. The goal is to find a unique 54 card deck. I want to know how many cards I should expect to pick up to find a full unique deck.

I am going to simulate multiple runs of picking up random cards until a full unique (54) deck is found to find an expected number of cards to find. 


## The Simulation
```{r}
n <- 10000 # number of simulations
set.seed(1234) 
full_deck <- 1:54 

sim_results <- c()

# run the simulation n times
for(x in seq(1, n)){
  card_count <- 0 # number cards found
  cards_found <- rep(FALSE, 54)
  # pick up cards until a unique deck is found, or reaches cap of 1000
  while (FALSE %in% cards_found & card_count < 1000){
    card <- sample(full_deck, size=1, replace=TRUE) # pick up a random card
    cards_found[card] <- TRUE # mark this card as found
    card_count <- card_count + 1
  }
  # add the count of cards picked up (unless it reached the cap)
  if(card_count < 1000){
    sim_results <- append(sim_results, card_count)
  }
}

head(sim_results)
```  

## Basic Stats
```{r}
# Checking if any runs reached the cap of 1000
print(length(sim_results))

# average or expected number of cards needed to pick up to get a full deck
print(mean(sim_results))

# Minimum number of cards found to get a full deck
print(min(sim_results))

# Maximum number of cards found to get a full deck
print(max(sim_results))
```
## Data Visualization
```{r}
hist(sim_results,
    main = "Histogram of Number of Cards Picked Up",
    xlab = "Number of Cards Picked Up")
```
